Measuring efficiency of the greedy-like heuristics for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization

### 2020-10-07 doc/paper.tex
work on C. section

	%  \subsection{Greedy Criterion based on Price-per-Unit}
	Concerning the greedy heuristic for the literature for solving WMSC problem~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
	\begin{align}
	g(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
	\end{align}
	where $f(s^p) = |\bigcup_{s \in s^p} s |$.
	This heuristic is also an approximation algorithm with $O(\log(n))$ approximation factor.

@@

      After conducting preliminary results, we decided to use the following parameters for our algorithms:
      \begin{itemize}
      	\item Greedy + Shaking parameters:  $\mathrm{DIST} = 5 \cdot \max_{i=0,...,n-1} d(v_i, v_{i+1})$, where $d$ represents the Euclidean distance, and $\mathrm{OFFSET} = 0.3$,
        \item Greedy + CPLEX parameters: $K = 0.05 \cdot n$. 
      \end{itemize}
	\subsection{Results and Discussion}

>>>>

	%  \subsection{Greedy Criterion based on Price-per-Unit}
	Concerning the greedy heuristic for the literature for solving WMSC problem~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following greedy rule:
	\begin{align}\label{eq:Lovasz}
	q_1(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
	\end{align}
	where $f(s^p) = |\bigcup_{s \in s^p} s |$.
	This heuristic is also an approximation algorithm with $O(\log(n))$ approximation factor.

@@

      After conducting preliminary results, we decided to use the following parameters for our algorithms:
      \begin{itemize}
      	\item Greedy + Shaking parameters:  $\texttt{DIST} = 5 \cdot \max_{i=0,...,n-1} d(v_i, v_{i+1})$, where $d$ represents the Euclidean distance, and $\texttt{OFFSET} = 0.3$,
        \item Greedy + CPLEX parameters: $K = 0.05 \cdot n$. 
      \end{itemize}
     The benchmark sets and the executable file of this project are provided at \href{link}{link}.
	\subsection{Results and Discussion}
        The following algorithms are included in our computation:
        \begin{itemize}
        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{CPLEX};
        \end{itemize}  and 9 heuristic approaches: 
           \begin{itemize}
           	\item three pure greedy methods, guided by $g_1$, $g_2$ and $g_3$ greedy criterion. We label them by \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
            \item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
            \item three \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy}-$i$+CPLEX, $i=1,2,3$, 
            where $i$ stands for heuristic $g_i$ involved as the greedy criterion of the hybrid;
           \end{itemize}
